---
title: "Plex Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---

```{r global, include = FALSE, cache = TRUE}
# Load data in global chunk so it's accessible
library(flexdashboard)
library(tidyverse)
library(httr)
library(httr2)
library(lubridate)
library(treemapify)
library(plotly)
library(shiny)
library(jsonlite)
library(DT)
library(RColorBrewer)
library(dropboxr)

getwd() %>% print()

source(here::here("R", "bootstrap.R"))
source_project("R", "lib", "getLastfm.R")
source_project("R", "lib", "getPlex.R")

getSlugs <- function(text) {
  text %>% 
    stringr::str_to_lower() %>% 
    stringr::str_remove_all(pattern = "[[:punct:]]") %>% 
    stringr::str_replace_all(pattern = "&", "and") %>% 
    stringr::str_replace_all(pattern = "\\s{2,}", replacement = " ") %>% 
    stringr::str_trim(side = "both") %>% 
    stringr::str_remove_all(pattern = "\\s\\(.*") %>% 
    stringr::str_replace_all(pattern = " ", replacement = "-")
}

apply_year_selection <- function(plex_data, year_choice) {
  if (is.null(year_choice) || year_choice == "All") {
    return(list(chooseYear = 3000, plexYear = plex_data))
  }

  if (stringr::str_detect(year_choice, "^1")) {
    min_year <- as.numeric(year_choice)
    max_year <- min_year + 9
    return(list(
      chooseYear = min_year,
      plexYear = dplyr::filter(plex_data, year >= min_year, year <= max_year)
    ))
  }

  selected_year <- as.numeric(year_choice)
  list(
    chooseYear = year_choice,
    plexYear = dplyr::filter(plex_data, year == selected_year)
  )
}

set_year_state <- function(rv, plex_data, year_choice) {
  year_state <- apply_year_selection(plex_data, year_choice)
  rv$chooseYear <- year_state$chooseYear
  rv$plexYear <- year_state$plexYear
}

artist_choices <- function(plex) {
  plex %>%
    dplyr::filter(!is.na(.data$albumArtist), .data$albumArtist != "Various Artists") %>%
    dplyr::distinct(.data$albumArtist) %>%
        dplyr::mutate(order = str_remove_all("^The ", albumArtist)) %>% 
    dplyr::arrange(.data$order) %>%
    dplyr::pull(.data$albumArtist)
}

complete_album_filter <- function(data) {
  data %>%
    dplyr::group_by(.data$album) %>%
    dplyr::filter(dplyr::n() >= max(.data$trackNum, na.rm = TRUE) - 3) %>%
    dplyr::ungroup()
}

# Use functions -----
removeEve <- function(lastfm) {
  lastfm <- lastfm %>% 
    filter(
      stringr::str_detect(artist, "Cocomelon", negate = TRUE),
      stringr::str_detect(artist, "Super Simple", negate = TRUE),
      stringr::str_detect(artist, "Duggee", negate = TRUE),
      stringr::str_detect(artist, "Lullaby", negate = TRUE),
      stringr::str_detect(artist, "Night Garden", negate = TRUE),
      stringr::str_detect(track, "Night Garden", negate = TRUE),
      stringr::str_detect(artist, "Toddler Tunes", negate = TRUE),
      stringr::str_detect(artist, "Pinkfong", negate = TRUE),
      stringr::str_detect(artist, "Idina Menzel", negate = TRUE),
      stringr::str_detect(artist, "Stephanie Beatriz", negate = TRUE),
      stringr::str_detect(artist, "Dwayne Johnson", negate = TRUE),
      stringr::str_detect(artist, "Bluey", negate = TRUE),
      stringr::str_detect(track, "Hey Gabby", negate = TRUE)
    )
}

plex <- getPlex(F)
lastfm <- getLastfm(F) %>% removeEve()


```

```{r}
rv <- reactiveValues(plex = plex,
                     lastfm = lastfm,
                     chooseYear = 3000,
                     plexYear = plex)

observeEvent(eventExpr = input$refreshPlex,
             handlerExpr = {
               showNotification("Updating Plex...")
               rv$plex <- getPlex(T)
               set_year_state(rv, rv$plex, input$chooseYear)
               shiny::updateSelectizeInput(
                 session,
                 inputId = "compareArtist",
                 choices = artist_choices(rv$plex),
                 selected = input$compareArtist,
                 server = TRUE
               )
               showNotification("Plex Updated!", type = 'message')
             })

observeEvent(eventExpr = input$refreshLastfm,
             handlerExpr = {
               showNotification("Updating Lastfm")
               rv$lastfm <- getLastfm(T) %>% removeEve()
               showNotification("Lastfm Updated!", type = 'message')
             })

observeEvent(eventExpr = input$chooseYear,
             handlerExpr = {
               set_year_state(rv, rv$plex, input$chooseYear)
             })
```

# Artist Comparison

## Artists Sidebar {.sidebar data-width="300"}

```{r}
shiny::radioButtons(
  inputId = "compareArtist",
  label = "Select artist",
  choices = artist_choices(plex),
  # options = list(placeholder = "Choose an artist"),
  selected = artist_choices(plex) %>% sample(1)
)
```

## Row {data-height="90"}

### 

```{r, out.width = "100%", fig.height = 0.5, eval = T}
renderPlot({
  progress <-  rv$plex %>%
      filter(albumArtist == input$compareArtist) %>%
      # filter(albumArtist == 'Damien Jurado') %>% 
    summarise(n1 = n(), n2 = sum(!is.na(rating))) %>% 
    transmute(perc = n2/n1, tot = 1-perc) %>% 
    gather() %>% rowwise() %>%  
    mutate(label = ifelse(test = key == 'perc', 
                          yes = str_c(round(100*value, 0), "%"), no = "")) %>% 
    ggplot(aes(x = 1, y = value, fill = rev(key), alpha = rev(key))) + 
    geom_col(position = 'fill', color = "#003EBB") + 
    coord_flip() + 
    scale_fill_manual(values = (c("#C1D1F4", "#003EBB"))) + 
    scale_alpha_manual(values = c(0.5, 1)) + 
    geom_label(aes(label = label, y = 0.9), size = 3, fill = 'white', linewidth = 0, fontface = 2)  + 
    theme_void()+ 
    theme(legend.position = 'none', 
          plot.background = element_rect(fill = 'white', color = 'white'),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank()) +
      ggtitle(input$compareArtist)
  # ggplotly(progress) %>% layout(height=80)
  progress
})

```

## Row

### Artist Albums

```{r}
DT::renderDataTable({
  req(input$compareArtist)

  artistAlbums <- rv$plex %>%
      filter(albumArtist == 'The Flaming Lips') %>% 
    # filter(albumArtist == input$compareArtist) %>%
    complete_album_filter() %>%
    group_by(album) %>%
    summarise(
      rated = sum(!is.na(rating)),
      total = n(),
      avRat = round(mean(rating, na.rm = TRUE) / 2, 2),
      year = suppressWarnings(max(year, na.rm = TRUE)),
      .groups = 'drop'
    ) %>%
    mutate(
      year = ifelse(is.infinite(year), NA, year),
      avRat = ifelse(is.nan(avRat), NA, avRat)
    ) %>%
    left_join(
      # rv$lastfm %>%filter(artist == input$compareArtist) %>%
          lastfm %>% filter(artist == 'The Flaming Lips') %>% 
        count(album, name = "Plays"),
      by = "album"
    ) %>%
    mutate(Plays = replace_na(Plays, 0)) %>%
    unite(col = 'n', rated, total, sep = "/") %>%
    arrange(desc(avRat), desc(Plays))

  # if (input$compareCompleteArtist) {
  #   artistAlbums <- artistAlbums %>%
  #     separate(col = 'n', into = c('rated', 'total'), sep = "/", remove = FALSE) %>%
  #     filter(rated == total) %>%
  #     select(-rated, -total)
  # }

  DT::datatable(artistAlbums, options = list(pageLength = 20))
})
```

## Row

### Ratings (circles)

```{r, eval = T}
renderPlot({
  req(input$compareArtist)
 
  plotData <- rv$plex %>%
      filter(albumArtist == input$compareArtist) %>% 
      select(albumArtist, album, track, trackNum, rating) %>% 
    complete_album_filter() %>%
    mutate(album = ifelse(nchar(album) > 24,
                          str_c(str_sub(album, 0, 22), "..."),
                          album)) %>%
    mutate(rating0 = replace_na(rating, 0)) %>%
    group_by(album) %>% 
    mutate(avRat = mean(rating, na.rm = T), count = n()) %>% 
      filter(count > 2) %>%  
    mutate(rating = rating0/2, avRat = avRat/2) %>% 
    mutate(title = album) %>% 
    arrange(title) %>% 
    mutate(title = forcats::fct_rev(title))

  if (nrow(plotData) == 0) {
    ggplot() +
      theme_void() +
      annotate("text", x = 0, y = 0, label = "No albums found for current artist")
  } else {
    plotData %>%
      ggplot(aes(x = trackNum, y = title, fill = rating)) +
      geom_point(shape = 21, size = 6) +
          scale_fill_gradient("",
                low = "#FFFFFF",   
                high = "#3c50b1",  
                limits = c(0, 5),  
                breaks = 0:5) +
      xlab(NULL) + ylab(NULL)
  }

})

```


### Ratings (lines)

```{r}
renderPlotly({
  req(input$compareArtist)
    
   plotData <- rv$plex %>%
    filter(albumArtist == input$compareArtist) %>%
    complete_album_filter() %>%
      filter(!is.na(rating)) %>% 
      distinct(album, track, rating, trackNum) %>%
      mutate(trackNum = suppressWarnings(as.numeric(trackNum))) %>%
      filter(!is.na(trackNum))
   
   numberOfAlbums <- length(unique(plotData$album))
   
   smoothPoints <- plotData %>% 
       group_by(album) %>% 
       arrange(trackNum, .by_group = TRUE) %>% 
       mutate(
         n = dplyr::n(),
         avRat = mean(rating),
         smooth = if (n() >= 4 && n_distinct(trackNum) >= 4) {
             fit <- loess(rating ~ trackNum, data = cur_data(), 
                          span = 0.75, degree = 2)
             predict(fit, newdata = cur_data()["trackNum"])
             } else {
                 avRat
                 }
       ) %>% 
       ungroup()
      
   plot_ly() %>% 
      plotly::add_lines(
          data = smoothPoints, showlegend = FALSE,
          x = ~trackNum, y = ~smooth/2, line = list(shape = "spline", smoothing = 2.2),
          color = ~album, 
          colors = colorRampPalette(brewer.pal(11, 'Spectral'))(numberOfAlbums)
      ) %>% 
       plotly::add_markers(
           data = plotData, 
           x = ~trackNum, y = ~rating/2, showlegend = FALSE,
           legendgroup = ~album, color = ~album,
           text = ~str_glue("{track} ({rating})<br>{album}"),
           opacity = 0.5, hoverinfo = 'text') %>% 
       plotly::layout(
           xaxis = list(title = NA, zeroline = FALSE),
           yaxis = list(title = NA, zeroline = FALSE)
       )
})
```

# Year comparison

## Sidebar {.sidebar data-width="250"}

```{r}
shiny::radioButtons(inputId = "chooseYear", label = "Select year:",
            choiceValues = c("All", '1950', '1960', '1970', '1980', '1990', 
    ## This used to be plex %>% na.omit %>% pull(year), can't remember why.
    c(2000:max(plex %>% filter(!is.na(year)) %>% pull(year)))), 
            choiceNames = c("All time", 
                            plex %>%
              filter(year >= 1950, albumArtist != 'Various Artists') %>% 
              mutate(choiceLabel = ifelse(
                year > 1999, year, 10*floor(year/10)
              )) %>% 
              distinct(albumArtist, album, choiceLabel) %>% 
              count(choiceLabel) %>% 
              arrange(choiceLabel) %>% 
              mutate(n = str_c("(", n, ")")) %>% 
              unite(choiceLabel, n, col = 'choiceLabel', sep = " ") %>% 
              pull(choiceLabel)),
              selected = max(plex$year, na.rm = TRUE)
)

actionButton(inputId = "refreshPlex", label = "Refresh Plex", icon = icon('refresh'))

actionButton(inputId = "refreshLastfm", label = "Refresh Lastfm", icon = icon("refresh"))
```

## Row 1 {data-height="50"}

### Rating Progress

```{r, out.width = "100%", fig.height = 0.5, eval = T}
renderPlot({
  progress <-  rv$plexYear %>% 
    summarise(n1 = n(), n2 = sum(!is.na(rating))) %>% 
    transmute(perc = n2/n1, tot = 1-perc) %>% 
    gather() %>% rowwise() %>%  
    mutate(label = ifelse(test = key == 'perc', 
                          yes = str_c(round(100*value, 0), "%"), no = "")) %>% 
    ggplot(aes(x = 1, y = value, fill = rev(key), alpha = rev(key))) + 
    geom_col(position = 'fill', color = "#003EBB") + 
    coord_flip() + 
    scale_fill_manual(values = (c("#C1D1F4", "#003EBB"))) + 
    scale_alpha_manual(values = c(0.5, 1)) + 
    geom_label(aes(label = label, y = 0.9), size = 3, fill = 'white', label.size = 0, fontface = 2)  + 
    theme_void()+ 
    theme(legend.position = 'none', 
          plot.background = element_rect(fill = 'white', color = 'white'),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank())
  # ggplotly(progress) %>% layout(height=80)
  progress
})

```

## Row table

### All albums

```{r}
shiny::checkboxInput(inputId = "onlyComplete", label = "Only include complete ratings", value = FALSE)
```

```{r, eval = T, out.width ="100%"}
DT::renderDataTable({
  data <- rv$plexYear %>% 
    filter(albumArtist != 'Various Artists') %>% 
    complete_album_filter() %>%
    group_by(albumArtist, album) %>% 
    summarise(x = n(), y = sum(!is.na(rating)),
              avRat = round(mean(rating, na.rm = TRUE) / 2, 2),
              .groups = 'drop') %>% 
    filter(x > 2) %>% 
    unite(col = 'match', albumArtist, album, sep = "-", remove = FALSE) %>% 
    mutate(match = getSlugs(match)) %>% 
    left_join(., 
              # rv$lastfm %>% 
              rv$lastfm %>% 
                unite(col = 'match', artist, album, sep = "-", remove = TRUE) %>% 
                mutate(match = getSlugs(match)) %>% 
                count(match, sort = T, name = 'Plays'),
              by = 'match') %>% 
    select(-match) %>% 
    arrange(desc(avRat)) %>% 
    unite(y, x, col = 'n', sep = "/")
    
  if (input$onlyComplete) {
    data <- data %>% 
      separate(col = 'n', sep = "/", into = c('x', 'y'), remove = FALSE) %>% 
      filter(x == y) %>% 
      select(-x, -y)
  }
  DT::datatable(data, options = list(
    bPaginate = TRUE
  ))
})

```

## Row table

### Top Songs

```{r, eval = T, out.width ="100%"}
DT::renderDataTable({
  data <- rv$plexYear %>% 
      select(artist, track, rating) %>% 
      filter(rating > 6) %>% 
    unite(col = 'match', artist, track, sep = "-", remove = FALSE) %>% 
    mutate(match = getSlugs(match)) %>% 
    left_join(., 
              # rv$lastfm %>%
              rv$lastfm %>%
                unite(col = 'match', artist, track, sep = "-", remove = TRUE) %>% 
                mutate(match = getSlugs(match)) %>% 
                count(match, sort = T, name = 'Plays'),
              by = 'match') %>% 
    select(-match) %>% 
    arrange(desc(rating), desc(Plays)) 
    
    DT::datatable(data, options = list(
        bPaginate = TRUE
        ))
})

```

## Row {data-height="50"}

### 

```{r}
shiny::checkboxInput(inputId = "onlyPlex", label = "Only include Plex", value = FALSE)
```

## Row

### Top Album Plays (Plex in blue)

```{r, eval = T}
renderPlot({
  
  if (rv$chooseYear == 3000) {
    ## Copy pretty much same as below, with entire lastfm history and entire plex library
    print ("All time")
    albums <- full_join(
      rv$lastfm %>%
        unite(col = 'match', artist, album, sep = "-", remove = FALSE) %>% 
        mutate(match = getSlugs(match)) %>% 
        count(artist, album, match, sort = T),
      rv$plex %>% 
        unite(col = 'match', albumArtist, album, sep = "-", remove = TRUE) %>% 
        mutate(match = getSlugs(match), inPlex = 1) %>%
        distinct(match, inPlex),
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = as.factor(inPlex),
             rank = row_number())
  } else if(rv$chooseYear >= 2006) {
    print("2006")
    # From 2006 onwards, take 25 most played albums from lastfm, see if they're in plex
    inPlex <- rv$plex %>% 
      unite(col = 'match', albumArtist, album, sep = " - ", remove = TRUE) %>% 
      mutate(match = getSlugs(match), inPlex = 1) %>% 
      distinct(match, inPlex)
    lastfmCount <- rv$lastfm %>% 
      filter(year(date) == as.numeric(input$chooseYear)) %>%
      unite(col = 'match', artist, album, sep = " - ", remove = FALSE) %>% 
      mutate(match = getSlugs(match)) %>% 
      count(artist, album, match, sort = T) 
    albums <- left_join(
      lastfmCount,
      inPlex,
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = forcats::as_factor(inPlex),
             rank = row_number())
    
    } else {
      # Before 2006 just take plex albums from that year and arrange by playcount
      plexCount <- rv$plexYear %>% 
        unite(col = 'match', albumArtist, album, sep = " - ", remove = FALSE) %>% 
        mutate(match = getSlugs(match), inPlex = 1) %>% 
        distinct(artist = albumArtist, album, match, inPlex)
    lastfmCount <- rv$lastfm %>% 
      unite(col = 'match', artist, album, sep = " - ", remove = TRUE) %>% 
      mutate(match = getSlugs(match)) %>% 
      count(match, sort = T)
    albums <- left_join(
      plexCount,
      lastfmCount,
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = forcats::as_factor(inPlex),
             rank = row_number())
        
    }
    
    albums %>% 
      purrr::when(
        input$onlyPlex ~ filter(., inPlex == 1),
        ~ .
      ) %>% 
      slice(1:25) %>% 
      unite(col = 'name', artist, album, sep = " - ") %>% 
      mutate(nchar = nchar(name)) %>% 
      mutate(name = ifelse(nchar > 47, str_c(str_sub(name, 0, 47), "..."), name)) %>% 
      mutate(name = forcats::fct_rev(forcats::fct_inorder(name))) %>% 
      ggplot(aes(x = name, y = n, fill = inPlex, group = inPlex)) + 
      geom_col(width = 0.7, color = "#003EBB") + 
      scale_fill_manual(values = c('white', "#809FDD"),
                        breaks = c(0, 1)) +
      theme(legend.position = 'none') +
      xlab(NULL) + ylab(NULL) +
      coord_flip()
})
```

### Track Plays (Plex in blue)

```{r, eval = T}
renderPlot({
  
  if (rv$chooseYear == 3000) {
    ## Copy pretty much same as below, with entire lastfm history and entire plex library
    print ("All time")
    tracks <- full_join(
      rv$lastfm %>%
        unite(col = 'match', artist, track, sep = "-", remove = FALSE) %>% 
        mutate(match = getSlugs(match)) %>% 
        count(artist, track, match, sort = T),
      rv$plex %>% 
        unite(col = 'match', artist, track, sep = "-", remove = TRUE) %>% 
        mutate(match = getSlugs(match), inPlex = 1) %>%
        distinct(match, inPlex),
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = as.factor(inPlex),
             rank = row_number())
  } else if(rv$chooseYear >= 2006) {
    print("2006")
    # From 2006 onwards, take 25 most played tracks from lastfm, see if they're in plex
    inPlex <- rv$plex %>% 
      unite(col = 'match', artist, track, sep = " - ", remove = TRUE) %>% 
      mutate(match = getSlugs(match), inPlex = 1) %>% 
      distinct(match, inPlex)
    lastfmCount <- rv$lastfm %>% 
      filter(year(date) == as.numeric(input$chooseYear)) %>%
      unite(col = 'match', artist, track, sep = " - ", remove = FALSE) %>% 
      mutate(match = getSlugs(match)) %>% 
      count(artist, track, match, sort = T)
    tracks <- left_join(
      lastfmCount,
      inPlex,
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = forcats::as_factor(inPlex),
             rank = row_number())
    
    } else {
      # Before 2006 just take plex albums from that year and arrange by playcount
      plexCount <- rv$plexYear %>% 
        unite(col = 'match', artist, track, sep = " - ", remove = FALSE) %>% 
        mutate(match = getSlugs(match), inPlex = 1) %>% 
        distinct(artist, track, match, inPlex)
    lastfmCount <- rv$lastfm %>% 
      unite(col = 'match', artist, track, sep = " - ", remove = TRUE) %>% 
      mutate(match = getSlugs(match)) %>% 
      count(match, sort = T)
    tracks <- left_join(
      plexCount,
      lastfmCount,
      by = 'match'
    ) %>% 
      arrange(desc(n)) %>% 
      mutate(inPlex = replace_na(inPlex, 0)) %>% 
      mutate(inPlex = forcats::as_factor(inPlex),
             rank = row_number())
        
    }
    
    tracks %>% 
      purrr::when(
        input$onlyPlex ~ filter(., inPlex == 1),
        ~ .
      ) %>% 
      slice(1:25) %>% 
      unite(col = 'name', artist, track, sep = " - ") %>% 
      mutate(nchar = nchar(name)) %>% 
      mutate(name = ifelse(nchar > 47, str_c(str_sub(name, 0, 47), "..."), name)) %>% 
      mutate(name = forcats::fct_rev(forcats::fct_inorder(name))) %>% 
      ggplot(aes(x = name, y = n, fill = inPlex, group = inPlex)) + 
      geom_col(width = 0.7, color = "#003EBB") + 
      scale_fill_manual(values = c('white', "#809FDD"),
                        breaks = c(0, 1)) +
      theme(legend.position = 'none') +
      xlab(NULL) + ylab(NULL) +
      coord_flip()
})
```

## Row

### Ratings 1

```{r, eval = T}
renderPlot({
  req(rv$plexYear)
 
  plotData <- rv$plexYear %>%
      select(albumArtist, album, track, trackNum, rating) %>% 
    # filter(albumArtist != 'Various Artists') %>% 
    complete_album_filter() %>%
    mutate(album = ifelse(nchar(album) > 24,
                          str_c(str_sub(album, 0, 22), "..."),
                          album)) %>%
    mutate(rating0 = replace_na(rating, 0)) %>%
    group_by(albumArtist, album) %>% 
    mutate(avRat = mean(rating, na.rm = T), count = n()) %>% 
      filter(count > 2) %>% 
    group_by(albumArtist, album, avRat) %>% 
    nest() %>%
    ungroup() %>%
    arrange(desc(avRat)) %>% 
    slice(1:50) %>% 
    unnest(cols = c(data)) %>% 
    mutate(rating = rating0/2, avRat = avRat/2) %>% 
    mutate(title = album) %>% 
    arrange(title) %>% 
    mutate(title = forcats::fct_rev(title))

  if (nrow(plotData) == 0) {
    ggplot() +
      theme_void() +
      annotate("text", x = 0, y = 0, label = "No albums found for current year filter")
  } else {
    plotData %>%
      ggplot(aes(x = trackNum, y = title, fill = rating)) +
      geom_point(shape = 21, size = 6) +
          scale_fill_gradient("",
                low = "#FFFFFF",   # Your vibrant light blue
                high = "#3c50b1",  # Your deep midnight blue
                limits = c(0, 5),  # Ensures the scale is always 0 to 5
                breaks = 0:5) +
      xlab(NULL) + ylab(NULL)
  }

})

```

### Ratings 2

```{r}
## Trying a new plot
renderPlot({
  colPal <- c('#FFFFFF', colorRampPalette(c("#B9E2FF", "#3c50b1"))(10))
  names(colPal) <- seq(from = 0, to = 5, by = 0.5)
  
  treemapData <- rv$plexYear %>% 
      select(album, rating, track) %>% 
      mutate(rating = replace_na(rating, 0),
             rating = round(rating / 2),
             n = 1) %>% 
      mutate(rating = forcats::as_factor(rating))
  
  treemap <- ggplot(treemapData, aes(area = n, fill = rating, 
                                     subgroup = album, subgroup2 = track)) +
      treemapify::geom_treemap() +
      treemapify::geom_treemap_subgroup_border(size = 5) +
      treemapify::geom_treemap_subgroup2_border(size = 0.5, color = 'light grey') +
      treemapify::geom_treemap_subgroup_text(place = 'center', alpha = 0.5, grow = T) +
      scale_fill_manual(values = colPal, 
                            breaks = c("0", "1", "2", "3", "4", "5"))
  treemap

    
})
```

# All albums

## Row {data-height="50"}

```{r}
shiny::checkboxInput(inputId = "complete2", label = "Only complete ratings", value = FALSE)
```

## Row {data-height="100"}

### 

```{r}
shiny::textInput(inputId = 'filterText', label = 'Search', value = '', width = "100%")
```

## Row

### 

```{r fig.height=96}

renderPlotly({
    colors <- c('#FFFFFF', '#6475C4', '#3B50B2')
  searchText <- if (is.null(input$filterText)) "" else input$filterText
  searchPattern <- getSlugs(searchText)

    filteredData <- rv$plex %>% 
        unite(albumArtist, album, col = 'filterText', sep = " ", remove = FALSE) %>% 
        mutate(filterText = getSlugs(filterText))

  if (nzchar(searchPattern)) {
    filteredData <- filteredData %>%
      filter(str_detect(string = filterText, pattern = searchPattern))
  }

    plotData <- filteredData %>% 
        select(-filterText) %>% 
      complete_album_filter() %>%
        purrr::when(
            input$complete2 ~ filter(., !is.na(sum(rating))),
            ~ .
        ) %>%
        ungroup() %>% 
        mutate(rating = ifelse(rating == 0, NA, rating)) %>% 
        group_by(album) %>% 
        mutate(y = n(), count = n()) %>% 
        filter(count > 2) %>% 
        na.omit() %>% 
        mutate(x = n()) %>% 
        group_by(albumArtist, album, x, y) %>% summarise(avRat = mean(rating) / 2, .groups = 'drop') %>% 
        # slice(1:25) %>% 
        arrange(avRat) %>% 
        mutate(album = str_c(album, " (", round(avRat, 2), ")")) %>% 
        mutate(album = forcats::fct_inorder(album)) %>% 
        mutate(compRat = (x/y)*avRat) %>% 
        select(-x, -y) %>% 
        gather(-album, -albumArtist, key = series, value = Rating)

if (nrow(plotData) == 0) {
  return(
    plotly::plot_ly() %>%
      layout(
        title = "No albums found for current filter",
        xaxis = list(visible = FALSE),
        yaxis = list(visible = FALSE)
      )
  )
}

album_count <- plotData %>%
  filter(series == 'avRat') %>%
  summarise(n = dplyr::n_distinct(album)) %>%
  pull(n)

if (is.na(album_count) || album_count < 1) {
  album_count <- 1
}

y_tick_size <- dplyr::case_when(
  album_count > 600 ~ 8,
  album_count > 250 ~ 9,
  album_count > 100 ~ 10,
  TRUE ~ 12
)

plot_height <- min(12000, max(350, album_count * 22))

margin_left <- 4 * max(nchar(as.character(plotData$album)), na.rm = TRUE)
margin_left <- ifelse(is.finite(margin_left), margin_left, 120)

plotly::plot_ly(plotData %>% filter(series == 'avRat'), 
                x = ~Rating, y = ~album, type = 'bar', orientation = 'h',
                text = ~str_c(albumArtist, ": ", album), hoverinfo = 'text',
                marker = list(color = colors[1], 
                              line = list(color = colors[2], width = 0.2))) %>% 
  add_trace(data = plotData %>% filter(series == 'compRat'),
            marker = list(color = colors[2]), hoverinfo = 'none') %>% 
  layout(xaxis= list(title = ""),
         yaxis = list(title = "",
                     tickfont = list(size = y_tick_size),
                     dtick = 1),
         showlegend = FALSE,
         barmode = 'overlay',
         margin = list(l = margin_left))

  # ggplot(aes(x = album, y = Rating, group = series, fill = series)) +
  # geom_col(position = 'identity', color = colors[3], size = 0.5, width = 0.7) +
  # scale_fill_manual(values = c(colors[1], colors[2])) + 
  # coord_flip() +
  # labs(x = NULL, y = NULL) +
  # theme(legend.position = 'none')
})
```
